### 2008-12-20 talk/ecoop2009/clibackend.tex
Standardize the footnote format.

When a new case is added to a flexswitch, the backend generates the new blocks
into a new single method.  The newly created method is pointed by a
delegate \footnote{\emph{Delegates} are the .NET equivalent of function
  pointers} stored in the flexswitch, so that it can be invoked later when
needed.

>>>>

When a new case is added to a flexswitch, the backend generates the new blocks
into a new single method.  The newly created method is pointed by a
delegate\footnote{\emph{Delegates} are the .NET equivalent of function
  pointers.} stored in the flexswitch, so that it can be invoked later when
needed.
